Rotations and Insecticide Resistance initial plots

### 2017-11-21 inst/documents/rotations_notes.Rmd
finishing migration but seem to have introduced bug, run_rot() failing

#high cost, no migration
run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 0.01 , rotation_interval = 10 , eff = 1 , dom_sel = 0.5 , dom_cos = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0 , cost = 0.1 , logy = FALSE )
#no cost, no migration
run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 0.01 , rotation_interval = 10 , eff = 1 , dom_sel = 0.5 , dom_cos = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0 , cost = 0 , logy = FALSE )
#no cost and rotate when resistant, no migration
run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 0.01 , rotation_interval = 0 , eff = 1 , dom_sel = 0.5 , dom_cos = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0 , cost = 0 , logy = FALSE )

@@

*21/11/17*

@@

~ is it worth creating a get_freq() or getraf() function similar to in rtsetse but not as complex ?
~ pass RAF
~ get_freq(insecticide=1, site='intervention', sex='f', gen=2 )
~ assume all for any not specified
~ have an as_df arg to return as a dataframe

>>>>

#high cost, no migration
run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 0.01 , rotation_interval = 10 , eff = 1 , dom_sel = 0.5 , dom_cos = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0 , cost = 0.1 , logy = FALSE )
#no cost, no migration
run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 0.01 , rotation_interval = 10 , eff = 1 , dom_sel = 0.5 , dom_cos = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0 , cost = 0 , logy = FALSE )
#no cost and rotate when resistant, no migration
run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 0.01 , rotation_interval = 0 , eff = 1 , dom_sel = 0.5 , dom_cos = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0 , cost = 0 , logy = FALSE )
#no cost, some migration
run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 0.01 , rotation_interval = 10 , eff = 1 , dom_sel = 0.5 , dom_cos = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0.05 , cost = 0 , logy = FALSE )

@@

*21/11/17*
~ is it worth creating a get_freq() or getraf() function similar to in rtsetse but not as complex ?
~ pass RAF
~ get_freq(insecticide=1, site='intervention', sex='f', gen=2 )
~ assume all for any not specified
~ have an as_df arg to return as a dataframe

@@

Fix this :
Error in filter(., active_or_refuge == "active") : 
  object 'active_or_refuge' not found
